30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex

@@

	As we saw in the previous section, we would like to have a decentralized anonymous network. This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us. Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry. These networks will be described in more detail in the next chapter. Among these networks are some overlay anonymous networks such as Tarzan.

@@

	\subsection{Browser based attacks}
		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis.

		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.

	\subsection{Replay Attacks}
		Hier wat over replay attacks

>>>>

		\subsection{Browser based attacks}
		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\

		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666. Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.

		\subsection{Replay Attacks}
			A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again. Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.

			Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship. On top of that, this attack can also be used as a denial of service attack. This attack is according to the authors quite challenging to solve and does require some further research.

@@

	As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network. This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us. Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry. These networks will be described in more detail in the next chapter. Among these networks are some overlay anonymous networks such as Tarzan.

@@
